Discovery of s-process stars in the LAMOST survey

### 2018-01-25 article/ms.tex
update abstract

\begin{abstract}
Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as `Barium stars'. While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many so-called Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars. These less-evolved stars are generally thought to have accreted mass from a more-evolved AGB companion. For this reason the frequency and properties of less-evolved Barium stars are uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution. Here we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST. Our sample includes; 257 Barium stars, 49 stars exhibiting only significant barium enhancement, and 661 exhibiting only strontium enhancement. This sample constitutes the largest number of s-process enhanced stars ever discovered, and represents the most comprehensive search for Barium stars in the Milky Way. All of our Barium stars are consistent with membership in the Milky Way disk, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory. We find 51 Barium stars exhibit some evidence of technetium, \todo{suggesting the existence of AGB stars in our sample}. Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature. However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium. \todo{A sentence about AGB yield comparison.} When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
\end{abstract}

>>>>

\begin{abstract}
Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as `Barium stars'. While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many so-called Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars. These less-evolved stars are generally thought to have accreted mass from a more-evolved AGB companion. For this reason the frequency and properties of less-evolved Barium stars are uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution. Here we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST. Our sample includes; 257 Barium stars, 49 stars exhibiting only significant barium enhancement, and 661 exhibiting only strontium enhancement. This sample constitutes the largest number of s-process enhanced stars ever discovered, and represents the most comprehensive search for Barium stars in the Milky Way. All of our Barium stars are consistent with membership in the Milky Way disk, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory. We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g} > 2$, which suggests they cannot be AGB stars and may indicate a recent ($100\,\textrm{Myr}$) mass accretion event. Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature. However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium. \todo{A sentence about AGB yield comparison.} When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
\end{abstract}
